|

### 2021-12-02 08-Discussion.Rmd
End of day:

## Chapter summary

@@

## Summary of principle findings

Overall, I did not identify a consistent effect of any blood lipid fraction (total cholesterol, LDL cholesterol, HDL cholesterol or triglycerides) on any dementia outcome (all-cause dementia, Alzheimer's disease or vascular dementia).

While published non-randomised studies provided evidence for a protective effect of statin use on Alzheimer's disease, this effect was not maintained when incorporated along with other sources of evidence in a quantitative triangulation framework. However, this equally may indicate that statins have a pleiotropic effects on Alzheimer's disease, that is an effect other than through lipid-lowering. However, this observed effect could also be due to reporting biases, a

## New evidence

## Summary of contributions

With respect to dementia epidemiology, the systematic review reported in Chapters

## Lessons learned

@@

@@

@@

#### Strengths

#### Weaknessess

## Implications of this research

### Clinical practice

@@

### Public health

@@

## Reproducible research

@@

@@

@@

>>>>

\newpage

### Chapter summary

@@

\newpage

### Lessons learned

@@

<!-- Systematic reviews should not be performed as part of a thesis, without suitable support and resourcing guaranteed. Assumption that everyone does a systematic review (without risk-of-bias assessments, inclusion of all literature, searching for other reviews) is foolish. -->

<!-- Average time to complete a s -->

<!-- However, new developments such as automated screening would allow for a reduced need for personnel to work on these things. [@pham2021] -->

@@

\newpage

### Reproducible research

\newpage

## Summary of clinical findings

### Effect of blood lipids on dementia outcomes

Overall, I did not identify a consistent effect of any blood lipid fraction (total cholesterol, LDL cholesterol, HDL cholesterol or triglycerides) on any dementia outcome (all-cause dementia, Alzheimer's disease or vascular dementia). 
While published non-randomised studies provided evidence for a protective effect of statin use on Alzheimer's disease, this effect was not maintained when incorporated along with other sources of evidence in a quantitative triangulation framework. However, this equally may indicate that statins have a pleiotropic effects on Alzheimer's disease, that is an effect other than through lipid-lowering. However, this observed effect could also be due to reporting biases, a

@@

\newpage

### Comparison with new evidence

&nbsp;<!----------------------------------------------------------------------->  
\newpage

### Implications for clinical practice

@@

\newpage

### Implications for public health

@@

\newpage

## Summary of methodological findings

### Preprint search tool
\newpage

### Inclusion of preprints
\newpage

### Risk of bias visualisation
\newpage

### Triangulation framework

\newpage

### Strengths

\newpage

### Weaknessess

\newpage

@@

&nbsp;<!----------------------------------------------------------------------->  
\newpage

@@

&nbsp;<!----------------------------------------------------------------------->  
\newpage

Opportunistic follow-up of established trials.

&nbsp;<!----------------------------------------------------------------------->  
\newpage

@@

&nbsp;
<!----------------------------------------------------------------------------->
\newpage

### 2021-12-02 front-and-back-matter/99-appendices.Rmd
Working version!
End of day:

<!-- TODO This needs to be split in two!  -->

@@

mx_data <- mx_api_content(to_date = "2019-09-01")

bx_data <- mx_api_content(server = "biorxiv",
                                    to_date = "2019-09-01")

>>>>

### Deviations from protocol

<!-- TODO Complete -->

* MR tool, actually used Mamluk

* ROB-ME

* No MCI, given size of dementia findings

* Sources of funding: Given that any bias introduced by sources of funding would operate , conflicts of interest and bias were considered seperate things here.[@sterne2013]

 * Dose response

@@

mx_data <- mx_api_content(to_date = "2019-07-01")

bx_data <- mx_api_content(server = "biorxiv",
                                    to_date = "2019-07-01")

### 2021-12-02 front-and-back-matter/_abstract.Rmd
End of day:

__Background__  
In the UK, an estimated 800000 people are currently living with dementia and this number is expected to double
by 2040. Despite the number of dementia cases and decades of research, there remains much unknown about
the pathogenesis and progression of the disease, and, at present, no effective treatment exists to arrest or
reverse the cognitive decline associated with the condition. In this context, identification of causal relationships
between modifiable targets and dementia risk is central to the development of evidence-based prevention
strategies and will be critically important in maintaining the long-term health of the ageing public. Blood lipid
levels have been implicated in the aetiology of dementia by genetic linkage and functional cell biology studies,
but current epidemiological evidence has yet to reach a consensus on their role in dementia risk.

>>>>

Identification of causal relationships between modifiable targets and risk of dementia is central to the development of evidence-based prevention strategies. Blood lipid levels have been implicated in the aetiology of dementia by genetic linkage and functional cell biology studies, but current epidemiological evidence has yet to reach a consensus on their role in dementia risk. This thesis sought to triangulate the causal effects of lipid levels on dementia (all-cause dementia, Alzheimer's disease and vascular dementia) risk using existing and new evidence.

I conducted four distinct analyses as part of this thesis. Firstly, a systematic review of 81 published and preprinted studies was used to summarise the existing evidence base. Preprinted studies were identified using a research tool developed as part of this thesis. I then supplemented the existing evidence via two primary studies: i) a cohort study of the association of lipid regulating agents and dementia incidence in the Clinical Practice Research Datalink (CPRD), and ii) an individual patient data meta-analysis of the association of blood lipids with dementia incidence in previously unanalysed cohorts accessed through the Dementia Platform UK. Finally, I used a novel quantitative triangulation framework to incorporate the results produced by the diverse methodological approaches while attempting to account for their respective biases and indirectness.

Overall I identified no consistent effect of any lipid fraction on any dementia outcome across the evidence sources presented in this thesis, through there was some suggestion of a protective effect of LDL-c lowering (via statin use) on all-cause dementia and Alzheimer's disease, and a harmful effect of raised triglyceride levels on vascular dementia. However, when assessed through the triangulation framework, both of these effects attenuated to the null. There was a noticeable absence of existing studies considering vascular dementia as an outcome, and

Future work should focus on defining
